Supplementary Information

### 2021-02-17 doc/manuscript/ForestGEO_treerings_SI.Rmd
rename files

all_GLS = "S35-S54"
GLS_BCNM = "S35"
GLS_BCNM_year = "S36"
GLS_HKK = "S37"
GLS_HKK_year = "S38"
GLS_SCBI = "S39"
GLS_SCBI_year = "S40"
GLS_LDW = "S41"
GLS_LDW_year = "S42"
GLS_HF = "S343"
GLS_HF_year = "S44"
GLS_ZOF = "S45"
GLS_ZOF_year = "S46"
GLS_NIO = "S47"
GLS_NIO_year = "S48"
GLS_LT = "S49"
GLS_LT_year = "S50"
GLS_CB = "S51"
GLS_CB_year = "S52"
GLS_SC = "S53"
GLS_SC_year = "S54"

@@

climwin_BCNM_W_legend = "Figure S15. Climwin output for water variable group at BCNM."
climwin_BCNM_T_legend = "Figure S16. Climwin output for temperature variable group at BCNM."
climwin_HKK_W_legend =  "Figure S17. Climwin output for water variable group at HKK."
climwin_HKK_T_legend = "Figure S18. Climwin output for temperature variable group at HKK."
climwin_SCBI_W_legend  = "Figure S19. Climwin output for water variable group at SCBI."
climwin_SCBI_T_legend = "Figure S20. Climwin output for temperature variable group at SCBI."
climwin_LDW_W_legend = "Figure S21. Climwin output for water variable group at LDW."
climwin_LDW_T_legend = "Figure S22. Climwin output for temperature variable group at LDW."
climwin_HF_W_legend =  "Figure S23. Climwin output for water variable group at HF."
climwin_HF_T_legend = "Figure S23. Climwin output for temperature variable group at HF."
climwin_ZOF_W_legend  = "Figure S25. Climwin output for water variable group at ZOF."
climwin_ZOF_T_legend = "Figure S26. Climwin output for temperature variable group at ZOF."
climwin_NIO_W_legend = "Figure S27. Climwin output for water variable group at NIO."
climwin_NIO_T_legend = "Figure S28. Climwin output for temperature variable group at NIO."
climwin_LT_W_legend =  "Figure S29. Climwin output for water variable group at LT."
climwin_LT_T_legend = "Figure S30. Climwin output for temperature variable group at LT."
climwin_CB_W_legend  = "Figure S31. Climwin output for water variable group at CB."
climwin_CB_T_legend = "Figure S32. Climwin output for temperature variable group at CB."
climwin_SC_W_legend  = "Figure S33. Climwin output for water variable group at SC."
climwin_SC_T_legend = "Figure S34. Climwin output for temperature variable group at SC."

@@

climwin_generic = "Rows correspond to the four different models run: (1) all $RW$ data, (2) $RW$ for the subset of cores for which $DBH could be reconstructed, (3) $BAI$, and (4)  $AGB$ growth. The first four columns give statistics for time windows tested in *climwin*, where window open and close indicate months prior to current August. Difference in $AIC$ relative to a model with no climate term (first column) is used to select the optimal time window (second column). The third and fourth columns give values of linear and quadratic terms for each time window. The final column shows the correlation of individual-level residuals to the selected climate variable, with the function fit in *climwin* (not the final fit)."

>>>>

all_GLS = "S35-S54"
GLS_BCNM = "S35"
GLS_BCNM_year = "S36"
GLS_HKK = "S37"
GLS_HKK_year = "S38"
GLS_SCBI = "S39"
GLS_SCBI_year = "S40"
GLS_LDW = "S41"
GLS_LDW_year = "S42"
GLS_HF = "S43"
GLS_HF_year = "S44"
GLS_ZOF = "S45"
GLS_ZOF_year = "S46"
GLS_NIO = "S47"
GLS_NIO_year = "S48"
GLS_LT = "S49"
GLS_LT_year = "S50"
GLS_CB = "S51"
GLS_CB_year = "S52"
GLS_SC = "S53"
GLS_SC_year = "S54"

@@

climwin_BCNM_W_legend = "Figure S15. Climwin output for water variable group at BCNM."
climwin_BCNM_T_legend = "Figure S16. Climwin output for temperature variable group at BCNM."
climwin_HKK_W_legend =  "Figure S17. Climwin output for water variable group at HKK."
climwin_HKK_T_legend = "Figure S18. Climwin output for temperature variable group at HKK."
climwin_SCBI_W_legend  = "Figure S19. Climwin output for water variable group at SCBI."
climwin_SCBI_T_legend = "Figure S20. Climwin output for temperature variable group at SCBI."
climwin_LDW_W_legend = "Figure S21. Climwin output for water variable group at LDW."
climwin_LDW_T_legend = "Figure S22. Climwin output for temperature variable group at LDW."
climwin_HF_W_legend =  "Figure S23. Climwin output for water variable group at HF."
climwin_HF_T_legend = "Figure S24. Climwin output for temperature variable group at HF."
climwin_ZOF_W_legend  = "Figure S25. Climwin output for water variable group at ZOF."
climwin_ZOF_T_legend = "Figure S26. Climwin output for temperature variable group at ZOF."
climwin_NIO_W_legend = "Figure S27. Climwin output for water variable group at NIO."
climwin_NIO_T_legend = "Figure S28. Climwin output for temperature variable group at NIO."
climwin_LT_W_legend =  "Figure S29. Climwin output for water variable group at LT."
climwin_LT_T_legend = "Figure S30. Climwin output for temperature variable group at LT."
climwin_CB_W_legend  = "Figure S31. Climwin output for water variable group at CB."
climwin_CB_T_legend = "Figure S32. Climwin output for temperature variable group at CB."
climwin_SC_W_legend  = "Figure S33. Climwin output for water variable group at SC."
climwin_SC_T_legend = "Figure S34. Climwin output for temperature variable group at SC."

@@

climwin_generic = "Rows correspond to the four different models run: (1) all $RW$ data, (2) $RW$ for the subset of cores for which $DBH could be reconstructed, (3) $BAI$, and (4)  $AGB$ growth. The first four columns give statistics for time windows tested in *climwin*, where window open and close indicate months prior to the last month in the climwin analysis window for the site (Table S1). Difference in $AIC$ relative to a model with no climate term (first column) is used to select the optimal time window (second column). The third and fourth columns give values of linear and quadratic terms for each time window. The final column shows the correlation of individual-level residuals to the selected climate variable, with the function fit in *climwin* (not the final fit)."
